---
title: "California Covid-19"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
runtime: shiny
---
<style>
body {
  max-width: 1800px;
  margin: 0 auto;
}
h1 {
  font-size: 50px;
  font-weight: 500;
}
.column {
  float: left;
  width: 50%;
}
.row{
  margin-left: 5%;
  margin-bottom: 50px;
}
.row:after {
  content: "";
  display: table;
  clear: both;
}
</style>

```{r setup, include=FALSE}
library(shiny)
library(data.table)
library(ggplot2)
library(dplyr)
library(flexdashboard)
library(leaflet)
library(curl)
library(knitr)
library(kableExtra)
library(plotly)
latimes.state.totals <- fread("https://raw.githubusercontent.com/datadesk/california-coronavirus-data/master/latimes-state-totals.csv", na.strings="?")
latimes.county.totals <- fread("https://raw.githubusercontent.com/datadesk/california-coronavirus-data/master/latimes-county-totals.csv")
cdph.race.ethnicity <- fread("https://raw.githubusercontent.com/datadesk/california-coronavirus-data/master/cdph-race-ethnicity.csv")
```

```{r, include=FALSE}
today = latimes.state.totals[1, "date"]
cases = latimes.state.totals[1, "confirmed_cases"]
new.cases = latimes.state.totals[1, "new_confirmed_cases"]
deaths = latimes.state.totals[1 , "deaths"]
new.deaths = latimes.state.totals[1, "new_deaths"]
```


Key Stats
=======================================================================

Row
-----------------------------------------------------------------------
  

### Stats: 
<div class="row">
  <div class="column">
<h3>Total number of confirmed cases:</h3>
<h1>`r cases`</h1>  
<h3>Daily number of confirmed cases:</h3>
<h1>`r new.cases`</h1>
  </div>
  <div class="column">
<h3>Total number of COVID-19 associated deaths:</h3>
<h1>`r deaths`</h1>
<h3>Daily number of COVID-19 associated deaths:</h3>
<h1>`r new.deaths`</h1>
  </div>
</div>

```{r, echo=FALSE}
tabledata = latimes.county.totals[1:117]
tabledata$fips <- NULL
tabledata$date <- NULL

scroll_box(kable(tabledata, col.names= c("County", "Confirmed cases", "Deaths", "New cases", "New deaths")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive", full_width = FALSE)), height='800px')
```


Plots
=======================================================================

Row
-----------------------------------------------------------------------

### Evolution of cases
```{r, echo=FALSE}
renderPlotly({
ggplotly(ggplot(latimes.state.totals) + 
  geom_line(aes(x=as.Date(date), y=confirmed_cases, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases)), size=1, color="red") +
  scale_x_date(date_labels = "%b",date_breaks = '1 month') +
  labs(x = "Date", 
       y = "Number of cases") +
  theme_minimal(), tooltip = "text")
})
```

### Evolution of deaths
```{r, echo=FALSE}
renderPlotly({
ggplotly(ggplot(latimes.state.totals) + 
  geom_line(aes(x=as.Date(date), y=deaths, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths)), size=1, color="black") +
  scale_x_date(date_labels = "%b",date_breaks = '1 month') +
  labs(x = "Date", 
       y = "Number of deaths") +
  theme_minimal(), tooltip = "text")
})
```


Row
-----------------------------------------------------------------------

### Cases per county
```{r, echo=FALSE}

renderPlotly({
ggplotly(ggplot(mapping=aes(color=county)) + 
  geom_line(data=filter(latimes.county.totals, county == input$county1), aes(as.Date(date), confirmed_cases, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county2), aes(as.Date(date), confirmed_cases, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county3), aes(as.Date(date), confirmed_cases, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county4), aes(as.Date(date), confirmed_cases, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county5), aes(as.Date(date), confirmed_cases, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases, '<br>County:', county))) +
  scale_x_date(date_labels = "%b",date_breaks = '1 month') +
  labs(x = "Date", 
       y = "Number of Cases") +
  theme_minimal(), tooltip = "text")
})
```

### Select counties
```{r, echo=FALSE, fig.width=1.6, fig.height=1}
selectInput("county1", label = "County 1:",
            choices = unique(latimes.county.totals$county), 
            selected = "Santa Clara",
            width = "155px")

selectInput("county2", label = "County 2:",
            choices = unique(latimes.county.totals$county), 
            selected = "San Diego",
            width = "155px")

selectInput("county3", label = "County 3:",
            choices = unique(latimes.county.totals$county), 
            selected = "Orange",
            width = "155px")
selectInput("county4", label = "County 4:",
            choices = unique(latimes.county.totals$county), 
            selected = "San Francisco",
            width = "155px")
selectInput("county5", label = "County 5:",
            choices = unique(latimes.county.totals$county), 
            selected = "Riverside",
            width = "155px")

```

### Deaths per county
```{r, echo=FALSE}

renderPlotly({
ggplotly(ggplot(mapping=aes(color=county)) + 
  geom_line(data=filter(latimes.county.totals, county == input$county1), aes(as.Date(date), deaths, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county2), aes(as.Date(date), deaths, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county3), aes(as.Date(date), deaths, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county4), aes(as.Date(date), deaths, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths, '<br>County:', county))) +
  geom_line(data=filter(latimes.county.totals, county == input$county5), aes(as.Date(date), deaths, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths, '<br>County:', county))) +
  scale_x_date(date_labels = "%b",date_breaks = '1 month') +
  labs(x = "Date", 
       y = "Number of death") +
  theme_minimal(), tooltip = "text")
})
```

Row
-----------------------------------------------------------------------

### Cases per age
```{r, echo=FALSE}

renderPlotly({
ggplotly(ggplot(mapping=aes(color=age)) + 
  geom_line(data=filter(cdph.race.ethnicity, age == input$age1 & race=="white"), aes(as.Date(date), confirmed_cases_total, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases_total, '<br>Age:', age))) +
  geom_line(data=filter(cdph.race.ethnicity, age == input$age2 & race=="white"), aes(as.Date(date), confirmed_cases_total, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases_total, '<br>Age:', age))) +
  geom_line(data=filter(cdph.race.ethnicity, age == input$age3 & race=="white"), aes(as.Date(date), confirmed_cases_total, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases_total, '<br>Age:', age))) +
  scale_x_date(date_labels = "%b %d",date_breaks = '10 days') +
  labs(x = "Date", 
       y = "Number of cases") +
  theme_minimal(), tooltip = "text")
})

```

### Select ages
```{r, echo=FALSE, fig.width=1.6, fig.height=1}
selectInput("age1", label = "Age 1:",
            choices = unique(c("0-17", "18-34", "35-49", "50-64", "65-79",  "80+")), 
            selected = "0-17",
            width = "155px")

selectInput("age2", label = "Age 2:",
            choices = unique(c("0-17", "18-34", "35-49", "50-64", "65-79",  "80+")), 
            selected = "50-64",
            width = "155px")

selectInput("age3", label = "Age 3:",
            choices = unique(c("0-17", "18-34", "35-49", "50-64", "65-79",  "80+")), 
            selected = "80+",
            width = "155px")
```

### Deaths per age
```{r, echo=FALSE}

renderPlotly({
ggplotly(ggplot(mapping=aes(color=age)) +
  geom_line(data=filter(cdph.race.ethnicity, age == input$age1 & race=="white"), aes(as.Date(date), deaths_total, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths_total, '<br>Age:', age))) +
  geom_line(data=filter(cdph.race.ethnicity, age == input$age2 & race=="white"), aes(as.Date(date), deaths_total, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths_total, '<br>Age:', age))) +
  geom_line(data=filter(cdph.race.ethnicity, age == input$age3 & race=="white"), aes(as.Date(date), deaths_total, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths_total, '<br>Age:', age))) +
  scale_x_date(date_labels = "%b %d",date_breaks = '10 days') +
  labs(x = "Date",
       y = "Number of deaths") +
  theme_minimal(), tooltip = "text")

})
```

Row
-----------------------------------------------------------------------

### Cases per race
```{r, echo=FALSE}

renderPlotly({
ggplotly(ggplot(mapping=aes(color=race)) + 
  geom_line(data=filter(cdph.race.ethnicity, age == "all" & race == input$race1), aes(as.Date(date), confirmed_cases_total, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases_total, '<br>Race:', race))) +
  geom_line(data=filter(cdph.race.ethnicity, age == "all" & race == input$race2), aes(as.Date(date), confirmed_cases_total, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases_total, '<br>Race:', race))) +
  geom_line(data=filter(cdph.race.ethnicity, age == "all" & race == input$race3), aes(as.Date(date), confirmed_cases_total, group=1, text = paste('Date: ', date, '<br>Cases:', confirmed_cases_total, '<br>Race:', race))) +
  scale_x_date(date_labels = "%b %d",date_breaks = '10 days') +
  labs(x = "Date", 
       y = "Number of cases") +
  theme_minimal(), tooltip = "text")
})
```

### Select races
```{r, echo=FALSE, fig.width=1.6, fig.height=1}
selectInput("race1", label = "Race 1:",
            choices = unique(c("asian", "black", "latino", "white", "other")), 
            selected = "asian",
            width = "155px")

selectInput("race2", label = "Race 2:",
            choices = unique(c("asian", "black", "latino", "white", "other")), 
            selected = "black",
            width = "155px")

selectInput("race3", label = "Race 3:",
            choices = unique(c("asian", "black", "latino", "white", "other")), 
            selected = "latino",
            width = "155px")
```

### Deaths per race
```{r, echo=FALSE}

renderPlotly({
ggplotly(ggplot(mapping=aes(color=race)) + 
  geom_line(data=filter(cdph.race.ethnicity, age == "all" & race == input$race1), aes(as.Date(date), deaths_total, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths_total, '<br>Race:', race))) +
  geom_line(data=filter(cdph.race.ethnicity, age == "all" & race == input$race2), aes(as.Date(date), deaths_total, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths_total, '<br>Race:', race))) +
  geom_line(data=filter(cdph.race.ethnicity, age == "all" & race == input$race3), aes(as.Date(date), deaths_total, group=1, text = paste('Date: ', date, '<br>Deaths:', deaths_total, '<br>Race:', race))) +
  scale_x_date(date_labels = "%b %d",date_breaks = '10 days') +
  labs(x = "Date", 
       y = "Number of deaths") +
  theme_minimal(), tooltip = "text")
})
```


Sources
=======================================================================

<h1>California Covid-19 Dashboard</h1>
This dashboard demonstrates some key stats about the Coronavirus pandemic in California.<br> It shows some data from: <br>
LA Times: https://github.com/datadesk/california-coronavirus-data/blob/master/latimes-state-totals.csv
<br>California Department of Public Health: https://github.com/datadesk/california-coronavirus-data/blob/master/cdph-race-ethnicity.csv
<br><br>
By John Bonchristiano<br>


